---
title: "Analysis of stop-flow respirometry data exported from ExpeData"
author: "Matias I. Munoz"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the data

I exported text files from ExpeData containing all the channels we recorded (e.g., O2, CO2, WVP, flow rate, etc...). These files were drift- an lag- corrected in ExpeData already (that's why the file names say "LagDrift" at the end. These are stored in a folder called "data".

```{r data}
# Folder containing the .txt files exported from ExpeData.
folder <- "/data/"

# Name of the file.
filename <- "Data_06-29-2025_001_DAY_LagDrift.txt" # n_frogs = 7, n_reps = 4
```

The file name can be changed for any of those in the "data" folder.

```{r}
# Load data frame.
df <- read.table(paste0(getwd(),folder, filename), sep = "\t", header = TRUE)
str(df)
head(df)
```

We transform seconds to minutes (divide by 60) and add a new column to the data frame:

```{r}
# Convert Seconds to Minutes and add new column called "Minutes"
df$Minutes <- df$Seconds/60
head(df)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
